Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-27 paper.tex
Fixing a few things

SOM is a type of unsupervised neural networks inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}. It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.

SOM is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric planes. Therefore, it could be used for different tasks like features reduction and data clustering and visualization.

Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer). Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e.; units). This means that every neuron is linked to every input in the input layer.

>>>>

SOM is a type of unsupervised neural network inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}. It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.
It is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric plane. Therefore, it could be used for different tasks such as feature selection and data clustering and visualization.

Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer). Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e. units). This means that every neuron is linked to every input in the input layer.
